DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-21 ase2017/paper.tex
captions

Control theory targets the construction of reliable systems by providing
mathematical guarantees about the stability and the performance of
closed-loop dynamics, where outputs of a discrete plant $G(z)$ are fed back
and compared to a reference signal towards which a controller $C(z)$ should
steer~\cite{astrom1997computer}.  Fig.~\ref{fig:typical-control-system}
depicts a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System}
\label{fig:typical-control-system}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{synthesis-flow.pdf}
\caption{Phases of the Controller Synthesis}
\label{fig:synthesis-flow}
\end{figure*}

@@

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant.}
  \label{tf-step-response}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant.}
  \label{ss-step-response}
\end{figure}

>>>>

Control theory targets the construction of reliable systems by providing
mathematical guarantees about the stability and the performance of
closed-loop dynamics, where outputs of a discrete plant $G(z)$ are fed back
and compared to a reference signal towards which a controller $C(z)$ should
steer~\cite{astrom1997computer}.  Fig.~\ref{fig:typical-control-system}
depicts a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical closed-loop control system}
\label{fig:typical-control-system}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.7\textwidth]{synthesis-flow.pdf}
\caption{Phases of the controller synthesis}
\label{fig:synthesis-flow}
\end{figure*}

@@

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{tf-step-response.eps}
  \caption{Step response for the Eq.~\eqref{tf-synth-controller} describing a stable system for the DC motor plant}
  \label{tf-step-response}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=0.5\textwidth]{ss-step-response.eps}
  \caption{Step response for the Eq.~\eqref{ss-synth-controller} describing a stable system for the pendulum plant}
  \label{ss-step-response}
\end{figure}
